Circumcision Paper Text

### 2024-04-12 paper/paper_cals.Rmd
Correct typos

<!-- TODO: Change year from 2020 to 2023 -->

@@

<!-- For VMMC countries, five year age group MC, MMC, TMC -->
For VMMC priority countries, five-year age group MC coverage 2006 was highest amongst 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
), but in 2020 was highest amongst
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(age_group)`
year olds, at
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
), respectively. 
This highlights both the increased prevalence of MC in VMMC priority countries, and the
downward shift in age profile of those who are circumcised, since VMMC programme 
implementation began. 
In 2006 MMC coverage was highest amongst 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
 year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
). 
This contrasts with 2020, where MMC coverage was highest amongst 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
 year olds, at
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
x
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
x
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
).
This shows that much of the downward shift in age profile of circumcised individuals since 2006 
has been "driven" by an increase in the number of MMCs performed amongst younger individuals. 
In 2006, TMC coverage was greatest in 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
). while in 2020 it was most prevalent in
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`.
This perhaps highlights that VMMC implementation has been focused on areas where 
TMC has not historically been widely prevalent, and so seems to have had little effect on patterns of TMC in 
VMMC priority countries, both in terms of its age profile and prevalence.

We can constrast this for the non-VMMC priority countries in SSA.
The five-year age group MC coverage in both 2006 and 2020 was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
) and 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
), respectively. 
This indicates that MC has increased slightly in non-VMMC priority countries, but the age profile (in terms of the five-year age group with the highest coverage) hasn't noticably changed. 
However, in 2006 MMC coverage was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
 year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
). 
This contrasts with 2020, where MMC coverage was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
 year olds, at
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
x
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
x
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
), showing an interesting shift upwards in age for MMCs in non-VMMC priority countries, as a result of VMMC focus on young adults, as well as a general increase in MMC coverage in these countries. 
In 2006, TMC coverage was greatest in 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
). while in 2020 it was most prevalent in
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`, highlighting a shift upwards in TMCs in VMMC priority countries, 
likely resulting from previously TMCs being performed as TMCs.

@@

Again, TMC coverage amongst both fifteen year age groups constrast to these increases for MC and MMC. 

@@

The mean age at circumcision for MC in 2006 was 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(upper)`
), while in 2020 it was
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(upper)`
).
<!-- Therefore, factoring in uncertainty there doesn't seem to have been a 
significant drop in mean age at MC from 2006 to 2020. -->
Similarly, the mean age at circumcision for MMC in 2006 was 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
), and in 2020 it was
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
).
<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
Finally, the mean age at circumcision in 2006 for TMC was 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
), and in 2020 it was
`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
However, it is important to note that the uncertainty ranges in our credible intervals 
overlap, so this increase could be seen as "non-significant", in some sense. 
In contrast, the mean age at circumcision for TMC was seen to decrease, altough again, 
not in a manor that exceeds our uncertainty bounds. 
This may suggest that VMMC implementation amongst 15-29 year olds has 
corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
replaced some circumcisions which would previously have been performed as TMCs, 
which may explain the observed decrease in mean age of TMC.

@@

The average TMC coverage in SSA in 2006 was 
`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
to 
x
`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
). 
This fell to 
`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
to 
x
`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, a decrease of 
`r to_percentage(tmc_cov$mean_tmc_cov_diff$mean)`. 
In non-VMMC priority countries, TMC coverage was 
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
to 
x
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
). 
This fell to 
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
to 
x
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, representing a decrease of 
`r to_percentage(tmc_cov_non_vmmc$mean_tmc_cov_diff$mean)`
.
In contrast, TMC coverage in VMMC priority countries was 
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
to 
x
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
). 
This fell to 
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
to 
x
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, representing a decrease of 
`r to_percentage(tmc_cov_vmmc$mean_tmc_cov_diff$mean)`.
Therefore, the decrease in TMC found throughout SSA is much more pronounced for 
non-VMMC countries.

@@

Amongst the 13 VMMC priority countries modelled, just 
x
 countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, 
x
 and 
x
. 
MC coverage across these countries increased from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020.

x
 (
x
 to 
x
) circumcisions were performed between 2007 and 2020 in these countries. 
Of these, 
x
 (
x
 to 
x
) were MMCs. 
No countries were e
x
pected to have reached this goal in all districts. 
The number of annual MCs increased from 
x
 (
x
 to 
x
) in 2006 to 
x
 (
x
 to 
x
) in 2020.

@@

However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries.

>>>>

<!-- TODO: Change year from 2020 to 2023 (once preprint is out) -->
<!-- TODO: Add survey stuff here -->
<!-- TODO: Add paragraph breaks (although that's not copying over from PDF) -->

@@

<!-- For VMMC countries, five year age group MC, MMC, TMC -->
For VMMC priority countries, five-year age group MC coverage 2006 was highest amongst 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
), but in 2020 was highest amongst
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(age_group)`
year olds, at
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
), respectively. 
This highlights both the increased prevalence of MC in VMMC priority countries, and the
downward shift in age profile of those who are circumcised, since VMMC programme 
implementation began. 
In 2006 MMC coverage was highest amongst 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
 year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
). 
This contrasts with 2020, where MMC coverage was highest amongst 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
 year olds, at
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
).
This shows that much of the downward shift in age profile of circumcised individuals since 2006 
has been "driven" by an increase in the number of MMCs performed amongst younger individuals. 
In 2006, TMC coverage was greatest in 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
). while in 2020 it was most prevalent in
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`.
This perhaps highlights that VMMC implementation has been focused on areas where 
TMC has not historically been widely prevalent, and so seems to have had little effect on patterns of TMC in 
VMMC priority countries, both in terms of its age profile and prevalence.

We can contrast this for the non-VMMC priority countries in SSA.
The five-year age group MC coverage in both 2006 and 2020 was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
) and 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
), respectively. 
This indicates that MC has increased slightly in non-VMMC priority countries, but the age profile (in terms of the five-year age group with the highest coverage) has not noticeably changed. 
However, in 2006 MMC coverage was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
 year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
). 
This contrasts with 2020, where MMC coverage was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
 year olds, at
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
), showing an interesting shift upwards in age for MMCs in non-VMMC priority countries, as a result of VMMC focus on young adults, as well as a general increase in MMC coverage in these countries. 
In 2006, TMC coverage was greatest in 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
). while in 2020 it was most prevalent in
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`, highlighting a shift upwards in TMCs in VMMC priority countries, 
likely resulting from previously TMCs being performed as TMCs.

@@

Again, TMC coverage amongst both fifteen year age groups contrast to these increases for MC and MMC. 

@@

The mean age at circumcision for MC in 2006 was 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(upper)`
), while in 2020 it was
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(upper)`
).
<!-- Therefore, factoring in uncertainty there doesn't seem to have been a 
significant drop in mean age at MC from 2006 to 2020. -->
Similarly, the mean age at circumcision for MMC in 2006 was 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
), and in 2020 it was
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
).
<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
Finally, the mean age at circumcision in 2006 for TMC was 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
), and in 2020 it was
`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
(
`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
- 
`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(upper)`
).
Therefore, the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
However, it is important to note that the uncertainty ranges in our credible intervals 
overlap, so this increase could be seen as "non-significant", in some sense. 
In contrast, the mean age at circumcision for TMC was seen to decrease, altough again, 
not in a manor that exceeds our uncertainty bounds. 
This may suggest that VMMC implementation amongst 15-29 year olds has 
corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
replaced some circumcisions which would previously have been performed as TMCs, 
which may explain the observed decrease in mean age of TMC.

@@

The average TMC coverage in SSA in 2006 was 
`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
to 
`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
). 
This fell to 
`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
to 
`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, a decrease of 
`r to_percentage(tmc_cov$mean_tmc_cov_diff$mean)`. 
In non-VMMC priority countries, TMC coverage was 
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
to 
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
). 
This fell to 
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
to 
`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, representing a decrease of 
`r to_percentage(tmc_cov_non_vmmc$mean_tmc_cov_diff$mean)`
.
In contrast, TMC coverage in VMMC priority countries was 
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
to 
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
). 
This fell to 
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
to 
`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, representing a decrease of 
`r to_percentage(tmc_cov_vmmc$mean_tmc_cov_diff$mean)`.
Therefore, the decrease in TMC found throughout SSA is much more pronounced for 
non-VMMC countries.

@@

As a reminder, in 2010 the WHO and UNAIDS set a 80\% MC target for 
15-49 year olds in the VMMC priority countries by 2018.
This target was expanded in 2016 to the new target of 90\% MC amongst 10-29 year olds 
in VMMC priority countries by 2021.

Amongst the 14 VMMC priority countries modelled, just 
x
 countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, 
x
 and 
x
. 
MC coverage across these countries increased from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020.

x
 (
x
 to 
x
) circumcisions were performed between 2007 and 2020 in these countries. 
Of these, 
x
 (
x
 to 
x
) were MMCs. 
No countries were expected to have reached this goal in all districts. 
The number of annual MCs increased from 
x
 (
x
 to 
x
) in 2006 to 
x
 (
x
 to 
x
) in 2020.

@@

However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority countries.
